---
title: "R Notebook"
output: html_notebook
---

```{r include=F}
library(datasets)
```


####Types of Data
numerical data - think real numbers

categirical data - think integers

binary data - think 0,1

modeling: predictor -> result

Linear model: numerical -> numerical 
```{r}
linearmodel <- lm(mpg ~ qsec, mtcars)
summary(linearmodel)
```


ANOVA model: categorical/binary -> numerical (note: categorical will be higher level ANOVA type model)
```{r}
ANOVAmodel <- lm(mpg ~ as.factor(cyl), mtcars)
summary.lm(ANOVAmodel)
```

Logit model: numerical -> binary/categorical (note: categorical will be higher level logit type model)
https://www.datacamp.com/community/tutorials/logistic-regression-R
```{r}
logitmodel <- glm(as.factor(vs) ~ mpg, mtcars, family = "binomial")
summary.lm(logitmodel)
```

Note: you can use multiple predictors and there are R tools to help you decide which predictors are the most effective -> algorithms which will test ALL combinations!

####Fitting Curves 
```{r}
#distributions - d,p,n,q in front of the dist name or abbrev 
curve(dnorm(x,0,1), xlim = c(-6, 6), ylab = 'Probablity Density, N(0,1)') #normal dist
curve(dt(x, df = 10), xlim = c(-6, 6), ylab = 'Probablity Density, t with 10 d.o.f.') #t-dist
```
